Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Add a missing ~ before \cite{}

Nell's overall story is a multi-character serial adventure, taking
cues from \textit{The Diamond Age} and
from the UNIVERSE narrative-generation system \cite{lebowitz:universe85}.
Each of the several characters represents a specific skill or subject
area, and each adventure represents about a year's curriculum.  This
design also improves modularity and allows updates and decentralized
authorship.

>>>>

Nell's overall story is a multi-character serial adventure, taking
cues from \textit{The Diamond Age} and
from the UNIVERSE narrative-generation system~\cite{lebowitz:universe85}.
Each of the several characters represents a specific skill or subject
area, and each adventure represents about a year's curriculum.  This
design also improves modularity and allows updates and decentralized
authorship.
